Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-08 paper.tex
Add point to conclusion regarding scaled physical model array predictions
Add figures

\begin{figure}
\centering
%\includegraphics[width=0.9\textwidth]{figures/turbine_coordinate_system}
\caption{Wake measurement coordinate system and locations. Dimensions are in
meters.} 
\label{fig:wake-locations}
\end{figure}

@@

\begin{figure}[ht]
\caption{Mean power (left) and drag (right) coefficient curves plotted for
multiple Reynolds numbers.}
\label{fig:perf-curves}
\end{figure}

@@

\begin{figure}[ht]
\caption{Mean power (left) and drag (right) coefficients at $\lambda=1.9$
plotted versus Reynolds number.} 
\label{fig:perf-Re-dep}
\end{figure}

@@

\todo[inline]{Add foil characteristics computed by XFOIL here.}

@@

\todo[inline]{Make bar graph for all $Re$.}

@@

\todo[inline]{Recreate the kinetic energy bar graph for all $Re$.}

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/turbine_coordinate_system}
\caption{Wake measurement coordinate system and locations. Dimensions are in
meters.} 
\label{fig:wake-locations}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.95\textwidth]{figures/perf_curves}
\caption{Mean power (left) and drag (right) coefficient curves plotted for
multiple Reynolds numbers.}
\label{fig:perf-curves}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.95\textwidth]{figures/perf_re_dep}
\caption{Mean power (left) and drag (right) coefficients at $\lambda=1.9$
plotted versus Reynolds number.} 
\label{fig:perf-Re-dep}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/all_foils_re_dep}
\caption{Foil section characteristics computed by XFOIL for various $Re_c$.}
\label{fig:foil-Re-dep}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/foil_kinematics_ct}
\caption{Geometric angle of attack (a), relative velocity (b) and torque coefficient
(c) calculated with a NACA 0020 foil.}
\label{fig:blade-kinematics}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{figures/cft_re_dep_foils}
\caption{Reynolds number depenence of the peak torque coefficient calculated via
static foil coefficients and blade kinematics.}
\label{fig:foils-C_T-Re-dep}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/mom_bar_graph}
\caption{Momentum transport quantities.}
\label{fig:mom-bar-graph}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
\caption{Mean kinetic energy transport quantities.}
\label{fig:K-bar-graph}
\end{figure}

@@

If using scaled physical models to predict array performance, it is important to
keep all turbines in the linear regime to avoid exaggerated power deficiencies
for downstream turbines, despite similarities in wake characteristics
